Parameter estimation

### 2023-04-25 SFE-article/Article_Model_Parameters.tex
25.04

% ---------------------------------------------------------------
% Preamble
% ---------------------------------------------------------------
%\documentclass[a4paper,fleqn,longmktitle]{cas-sc}
\documentclass[a4paper,fleqn]{cas-dc}
%\documentclass[a4paper]{cas-dc}
%\documentclass[a4paper]{cas-sc}
% ---------------------------------------------------------------
% Make margins bigger to fit annotations. TO be removed later
\paperwidth=\dimexpr \paperwidth + 6cm\relax
\oddsidemargin=\dimexpr\oddsidemargin + 3cm\relax
\evensidemargin=\dimexpr\evensidemargin + 3cm\relax
%\marginparwidth=\dimexpr \marginparwidth + 3cm\relax
% -------------------------------------------------------------------- 
% Packages
% --------------------------------------------------------------------
% Figure packages
\usepackage{graphicx,float}
\usepackage{adjustbox}
% Text, input, formatting, and language-related packages
\usepackage[T1]{fontenc}
\usepackage{subcaption}
\usepackage[bordercolor=gray!20,backgroundcolor=blue!10,linecolor=black,textsize=footnotesize,textwidth=1in]{todonotes}
\setlength{\marginparwidth}{1in}
% \usepackage[utf8]{inputenc}
% \usepackage[nomath]{lmodern}

@@

% ===================================================
% ABSTRACT
% ===================================================
\begin{abstract}
%Given a system of partial differential equations, $F(t,x,\dot{x},p,u)=0$, where $x$ represents state variables, $p$ is the parameters, and $u$ are control variables, the process model is simultaneously solved for both $x_i$ and a set of sensitivity functions, $dx_i/dp_j$, overall times $t$.These sensitivity functions measure the influence of the parameter change on the model's output. As an example, the supercritical extraction process is presented. The impact of mass flow rate, pressure, and inlet temperature on the model's output is discussed. The sensitivity analysis results prove that the considered variables can affect the extraction's yield and be used as control variables in optimization problems. Moreover, the local sensitivity analysis results are analyzed from a phenomenological point of view to enhance understanding of the process model.
%Given a system of partial differential equations, $F(t,x,\dot{x},\Theta,u)=0$, where $x$ represents state variables, $\Theta$ are the parameters, and $u$ are control variables, we describe the supercritical extraction process. The process model describes a partially filled extractor with a fixed bed, which work under constant operating conditions. We assume that the flow is uniform across any cross-section, although the area available for the fluid phase can change along the extractor. We apply the concept of quasi-one-dimensional flow to mimic the modelling of a two-dimensional case.
%In this work, a distributed-parameter model, based on \citet{Reverchon1996} is used to describe a fluid-solid extraction process of caraway oil from caraway seeds with $CO_2$ as a solvent. The model parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient \textit{and saturation concentration} are obtained from parameter estimation. The parameters are estimated based on four experiments performed at $40^\circ C$/$200$ bar, $50^\circ C$/$200$ bar, $40^\circ C$/$300$ bar and $50^\circ C$/$300$ bar. Given yield data, the model-based parameter estimation uses the maximum likelihood estimation method under assumption of normal error.
We consider a system of partial differential equations, $F(t,x,\dot{x},\Theta,u)=0$, where $x$ denotes the state variables, $\Theta$ represents the parameters, and $u$ is the control variables. Our focus is on the supercritical extraction process, which involves a partially filled extractor with a fixed bed that operates under constant conditions. We assume the flow is uniform across any cross-section, although the area available for the fluid phase can vary along the extractor. To model this two-dimensional case, we use the concept of quasi-one-dimensional flow.
To describe the fluid-solid extraction process of caraway oil from caraway seeds with $CO_2$ as a solvent, we use a distributed-parameter model based on \citet{Reverchon1996}. This model requires parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient, and saturation concentration. We estimate these parameters from four experiments at different temperatures and pressures: $40^\circ C$/$200$ bar, $50^\circ C$/$200$ bar, $40^\circ C$/$300$ bar, and $50^\circ C$/$300$ bar. We obtain the parameter values using the maximum likelihood estimation method on yield data under the normal error assumption.

@@

@@

\begin{figure*}[!h]
	%\centering 
	\includegraphics[trim=0cm 6cm 0cm 0cm, clip,height=0.9\textheight]{Sections/ultraReportT5.pdf}
	\caption{The result of solid density measurement}
\end{figure*}

>>>>

% ---------------------------------------------------------------
% Preamble
% ---------------------------------------------------------------
%\documentclass[a4paper,fleqn,longmktitle]{cas-sc}
\documentclass[a4paper,fleqn]{cas-dc}
%\documentclass[a4paper]{cas-dc}
%\documentclass[a4paper]{cas-sc}
% ---------------------------------------------------------------
% Make margins bigger to fit annotations. TO be removed later
\paperwidth=\dimexpr \paperwidth + 6cm\relax
\oddsidemargin=\dimexpr\oddsidemargin + 3cm\relax
\evensidemargin=\dimexpr\evensidemargin + 3cm\relax
%\marginparwidth=\dimexpr \marginparwidth + 3cm\relax
% -------------------------------------------------------------------- 
% Packages
% --------------------------------------------------------------------
% Figure packages
\usepackage{graphicx,float}
\usepackage{adjustbox}
% Text, input, formatting, and language-related packages
\usepackage[T1]{fontenc}
\usepackage{subcaption}

\usepackage{csvsimple}

\usepackage[bordercolor=gray!20,backgroundcolor=blue!10,linecolor=black,textsize=footnotesize,textwidth=1in]{todonotes}
\setlength{\marginparwidth}{1in}
% \usepackage[utf8]{inputenc}
% \usepackage[nomath]{lmodern}

@@

% ===================================================
% ABSTRACT
% ===================================================
\begin{abstract}
%Given a system of partial differential equations, $F(t,x,\dot{x},p,u)=0$, where $x$ represents state variables, $p$ is the parameters, and $u$ are control variables, the process model is simultaneously solved for both $x_i$ and a set of sensitivity functions, $dx_i/dp_j$, overall times $t$.These sensitivity functions measure the influence of the parameter change on the model's output. As an example, the supercritical extraction process is presented. The impact of mass flow rate, pressure, and inlet temperature on the model's output is discussed. The sensitivity analysis results prove that the considered variables can affect the extraction's yield and be used as control variables in optimization problems. Moreover, the local sensitivity analysis results are analyzed from a phenomenological point of view to enhance understanding of the process model.
%Given a system of partial differential equations, $F(t,x,\dot{x},\Theta,u)=0$, where $x$ represents state variables, $\Theta$ are the parameters, and $u$ are control variables, we describe the supercritical extraction process. The process model describes a partially filled extractor with a fixed bed, which work under constant operating conditions. We assume that the flow is uniform across any cross-section, although the area available for the fluid phase can change along the extractor. We apply the concept of quasi-one-dimensional flow to mimic the modelling of a two-dimensional case.
%In this work, a distributed-parameter model, based on \citet{Reverchon1996} is used to describe a fluid-solid extraction process of caraway oil from caraway seeds with $CO_2$ as a solvent. The model parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient \textit{and saturation concentration} are obtained from parameter estimation. The parameters are estimated based on four experiments performed at $40^\circ C$/$200$ bar, $50^\circ C$/$200$ bar, $40^\circ C$/$300$ bar and $50^\circ C$/$300$ bar. Given yield data, the model-based parameter estimation uses the maximum likelihood estimation method under assumption of normal error.
We consider a system of partial differential equations, $G(t,x,\dot{x},\Theta,u)=0$, where $x$ denotes the state variables, $\Theta$ represents the parameters, and $u$ is the control variables. Our focus is on the supercritical extraction process, which involves a partially filled extractor with a fixed bed that operates under constant conditions. We assume the flow is uniform across any cross-section, although the area available for the fluid phase can vary along the extractor. To model this two-dimensional case, we use the concept of quasi-one-dimensional flow.
To describe the fluid-solid extraction process of caraway oil from caraway seeds with $CO_2$ as a solvent, we use a distributed-parameter model based on \citet{Reverchon1996}. This model requires parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient, and saturation concentration. We estimate these parameters from four experiments at different temperatures and pressures: $40^\circ C$/$200$ bar, $50^\circ C$/$200$ bar, $40^\circ C$/$300$ bar, and $50^\circ C$/$300$ bar. We obtain the parameter values using the maximum likelihood estimation method on yield data under the normal error assumption.

@@

\subsection{Initial and boundary conditions} \label{CH: IC_BC}
\subfile{Sections/IC_BC}

@@

\begin{figure*}[!h]
	%\centering 
	\includegraphics[trim=0cm 6cm 0cm 0cm, clip,height=0.85\textheight]{Sections/ultraReportT5.pdf}
	\caption{The result of solid density measurement}
\end{figure*}

{\footnotesize
	\begin{equation*}
		\rho_s^{ave} = \frac{1.2585+1.2582+1.2561+1.2546+1.2555}{5} = 1.25658 [g/cc]
	\end{equation*}
}

### 2023-04-25 SFE-article/Sections/Experiments.tex
25.04

	The close the optimization problem given by a set of equations \ref{EQ: Optimization_formulation_MLE}, it is required to know the dataset $Y(t)$. In this case, the dataset has been obtained by performing the extraction of caraway oil from caraway seeds. The caraway seeds have been obtained from the company Caraway Finland\todo{Should be mentioned?} during the 2022 growing season. The caraway seeds have been pre-treated with Retsch SM 300 cutting mill to decrease the particle size to 1mm and break the outer shell of the seeds. Later, the moisture content was analysed to ensure that it does not have a negative effect on the extraction process. An Infrared Moisture Analyser was used to investigate the sample. The moisture content after grinding was 4.83\%. The grind material density was measured by pycnometer and its result can be found in appendix \ref{CH: Solid_Density_Measurment}. Moreover, the porosity was calculated to be 0.5, as explained in appendix \ref{CH: Porosity}.

	The unit used for the experimental work is a 10-liter extractor \todo{Should Biorukki be mentioned?} with an inner diameter of around 15 cm and 60 cm height \todo{Double check dimension}. Four experiments have been performed in that unit at the following operating conditions: $40^\circ C / 200$ bar, $50^\circ C / 200$ bar, $40^\circ C / 300$ bar and $50^\circ C / 300$ bar. 1 kg (or 1.6 liters) of grind material was weighed and placed in the extraction chamber. Due to technical limitations, the amount of solid material for extraction was selected to be 1 kg per batch, which is not sufficient to fill the whole chamber.

	After the material was loaded into the chamber, the extractor is pre-heated to desired temperature. The next step is to close the outlet line coming out of the extractor and fill the extraction chamber with $CO_2$. The $CO_2$ is pumped and compressed until the operating pressure is achieved. When the operating temperature and pressure are obtained, the outlet in is open to allow the solvent to flow through the system. The solvent extracts essential oils from the fixed bed of solid material and the mixture $CO_2$-oil flow from the extractor to the separator. The separator was operating at $50^\circ C$ and $50$ bar. At this condition, the gasified $CO_2$ leaves from the top, while oil stays in the liquid form and is collected at the bottom of the separator. Every 5 minutes, the oil is drained from the separator, and its weight is measured. The amount of oil collected during a batch is an output of the experiment and it is used as data for parameter estimation. The extraction time for each batch was 150 minutes, counted from the opening of the extractor outlet port.

@@

	\begin{table}[tbh!]

>>>>

	In order to solve the optimization problem presented in equation \ref{EQ: Optimization_formulation_MLE}, it is necessary to have knowledge of the dataset $Y(t)$, which was obtained by extracting caraway oil from caraway seeds. To prepare the seeds for extraction, they were first pre-treated using a Retsch SM 300 cutting mill to reduce their particle size to 1mm and break their outer shell. The moisture content of the seeds was then determined using an Infrared Moisture Analyser, which revealed an average moisture content of 4.83\% in the solid particles after grinding. Next, the density of the solid material was measured using a pycnometer, which can be found in appendix \ref{CH: Solid_Density_Measurment}. Finally, the material's porosity was also calculated to be 0.5, as explained in appendix \ref{CH: Porosity}.

	The caraway seeds used in the experiments were obtained from Caraway Finland during the 2022 harvesting season. The experiments were conducted using a 10-litre extractor with an inner diameter of approximately 15 cm and a height of 60 cm, which was rented from VTT Bioruukki. Four experiments were performed under different operating conditions: $40^\circ C / 200$ bar, $50^\circ C / 200$ bar, $40^\circ C / 300$ bar, and $50^\circ C / 300$ bar. The volumetric flow rate used in all experiments was 0.4 litres per minute, with negligible variations. The amount of solid material used for extraction was 1 kg (or 1.6 litres), which was not enough to fill the entire extraction chamber.

	After loading the material into the chamber, the extractor was pre-heated to the desired temperature. The outlet line was then closed, and the extraction chamber was filled with $CO_2$. The $CO_2$ was pumped and compressed until the desired operating pressure was reached. When the operating temperature and pressure were achieved, the outlet line was opened, allowing the solvent to flow through the system. The solvent extracted the essential oils from the solid material, and the resulting $CO_2$ and oil mixture flowed from the extractor to the separator. The separator operated at $50^\circ C$ and $50$ bar, with gaseous $CO_2$ exiting from the top and oil remaining at the bottom. The extraction time for each batch was 150 minutes, measured from the opening of the extractor outlet port. Every 5 minutes, the oil was drained from the separator, and its weight was measured. The resulting time series $Y(t)$ corresponds to the output of measurement equation \ref{Model_measurment_1} and can be used for parameter estimation.

@@

	\begin{table}[!h]

### 2023-04-25 SFE-article/Sections/Model.tex
25.04

	\subsubsection{Continuity equation} \label{CH: Continuity}
	The continuity equation for the fluid phase is derived in Appendix \ref{CH: Gouverning equations}. When the cross-sectional area of the channel $A_f$ is specified as a function of the void fraction ${\color{magenta}\phi}(z)$ (where ${\color{magenta}\phi}$ is the void fraction of the bed and $A$ is the cross-section of the empty extractor), the continuity equation takes the form: \todo[]{assign a color to v and u}

@@

		\subsubsection{State-space representation} \label{CH: State_space}
		It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content ${\color{magenta}c_s_0}$. Moreover, it is considered that the initial temperature of the extractor in every place is equal to ${\color{magenta}h_0}$. Therefore, the initial conditions employed in the simulation are:

		{\footnotesize
			\begin{subequations}
				\begin{align*}
					{\color{blue}c_f}(t = 0, z) &= 0   \\
					{\color{blue}c_s}(t = 0, z) &= {\color{magenta}c_s_0} \\
					{\color{blue}h}(t = 0, z) &= {\color{magenta}h_0}
				\end{align*}
		\end{subequations} }

>>>>

	\subsubsection{Continuity equation} \label{CH: Continuity}
	The continuity equation for the fluid phase is derived in Appendix \ref{CH: Gouverning equations}. When the cross-sectional area of the channel $A_f$ is specified as a function of the void fraction ${\color{magenta}\phi}(z)$ (where ${\color{magenta}\phi}$ is the void fraction of the bed and $A$ is the cross-section of the empty extractor), the continuity equation takes the form: \todo[]{assign a color of v and u}

@@

		\subsubsection{State-space representation} \label{CH: State_space}
		It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content ${\color{magenta}c_{s0}}$. The fluid concentration is assumed to not be uniform, and as such it is described by a function $H=H(z)$. The further discussion on the distribution of concentration in the fluid phase can be found in appendix \todo[fancyline]{REF}. Moreover, it is considered that the initial temperature of the extractor in every place is the same and described by ${\color{magenta}h_0}$. Therefore, the initial conditions employed in the simulation are:

		{\footnotesize
			\begin{subequations}
				\begin{align*}
					{\color{blue}c_f}(t = 0, z) &= H(z)   \\
					{\color{blue}c_s}(t = 0, z) &= {\color{magenta}c_{s0}} \\
					{\color{blue}h}(t = 0, z) &= {\color{magenta}h_0}
				\end{align*}
		\end{subequations} }

### 2023-04-25 SFE-article/Sections/Parameter_estimation.tex
25.04

However, obtaining analytical solutions for a deterministic process model can be challenging, so experiments are often conducted where the vector of derivatives $dY(t_i)/dt$ is measured instead of $Y(t_i)$ itself. In such cases, it is assumed that the unobservable error is added to the deterministic derivative $dy(\theta, t_i)/dt$ (as shown in equation \ref{Model_measurment_2}) as follows:

{\footnotesize
	\begin{equation*}
		\cfrac{d Y(t_i)}{dt} = \cfrac{dy(\theta, t_i)}{dt} + \epsilon(t_i)
\end{equation*} }

@@

Examination of Equation \ref{EQ: Measurment_noise} shows that $ Y(t_i)$ depends only on $t_i$, $\theta$ and $\epsilon(t_i)$ and is not conditioned by any previous measurement. Consequently, we can write

@@

		\todo{$x$ has not been defined}

>>>>

However, obtaining analytical solutions for a deterministic process model can be challenging, so experiments are often conducted where the vector of derivatives $dY(t_i)/dt$ is measured instead of $Y(t_i)$ itself. In such cases, it is assumed that the unobservable error is added to the deterministic derivative $dy(\theta, t_i)/dt$ as shown below

{\footnotesize
	\begin{equation}  \label{EQ: Measurment_noise}
		\cfrac{d Y(t_i)}{dt} = \cfrac{dy(\theta, t_i)}{dt} + \epsilon(t_i)
\end{equation} }

@@

Examination of Equation \ref{EQ: Measurment_noise} shows that $ d Y(t_i) / dt$ depends only on $t_i$, $\theta$ and $\epsilon(t_i)$ and is not conditioned by any previous measurement. Consequently, we can write

@@

### 2023-04-25 SFE-article/Sections/Results.tex
25.04

    The parameter estimation problem was solved by fitting the process model to the dataset \ref{tab: Yield_data}. Each time-series was fitted to the model separately. As a result of fitting, the following parameters were obtained:

    \begin{itemize}
        \item Partition coefficient $k_m$
        \item Internal Diffusion coefficient $D_i$
        \item Axial Diffusion coefficient $D_e^M$
        \item Standard Deviation $\sigma$
    \end{itemize}

    Moreover, the initial state estimation was performed together with parameter estimation. The concentration of solute is assumed to be constant and uniformly distributed. On the other hand, the solute concentration is assumed not to be uniform and not zero, which is a common assumption. During the preparation period, when the operating conditions are achieved, the solute diffuses to the fluid phase in contact with the solid particles. Later, the solute in the fluid phase is partially moved (if the pressure increase in the system, the pump cause the movement of the fluid, even if the outlet valve is closed) to the region where there is no solid phase. As a result, the solute distribution in the fluid phase should also be estimated as it is unknown. Some conclusions can be drawn from the analysis of the initial part of each yield curve. It can be noticed that each curve at the beginning has a curvature, which is not linear. In a general sense, it can be said that a quadratic function could approximate the initial part of each extraction curve. A function that, after integration, gives a quadratic-like result is a straight line. Based on that observation, the solute concentration in the fluid phase is assumed to be linearly distributed. The solute concentration is assumed to be zero at the outlet and reach the maximum at the beginning of the fixed bed. Such a formulation allows to fully describe the linear distribution of solute in the solid phase if the total mass of solute in the fluid phase is known, as explained in appendix \todo[]{Add chapter}. The total mass of solute in the fluid phase can be obtained from the total mass of solute $m_{total}$ and partition coefficient $\tau$, which is defined as

    {\footnotesize
    \begin{equation*}
        \tau = \cfrac{\text{total mass of solute in the fluid phase}}{\text{total mass of solute in the system}} = \cfrac{m^0_{fluid}}{m_{total}}
    \end{equation*}
    }

@@

    \begin{itemize}
        \item Total mass of solute $m_{total}$
        \item Partition coefficient $\tau$
    \end{itemize}

	Some results of the parameter estimations

	\begin{figure*}
		\centering
		\begin{subfigure}[b]{0.7\textwidth}
			\centering
			\includegraphics[trim = 3cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P200.pdf}
			\caption{Experiment at $40^\circ C$ and $200$ bar}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.7\textwidth}
			\centering
			\includegraphics[trim = 3cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P200.pdf}
			\caption{Experiment at $50^\circ C$ and $200$ bar}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.7\textwidth}
			\centering
			\includegraphics[trim = 3cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P300_org.pdf}
			\caption{Experiment at $40^\circ C$ and $300$ bar}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.7\textwidth}
			\centering
			\includegraphics[trim = 3cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P300_org.pdf}
			\caption{Experiment at $50^\circ C$ and $300$ bar}
		\end{subfigure}
		\caption{Results of parameter fitting, with estimation of the initial state}
	\end{figure*}

	\begin{figure*}
	\centering
	\begin{subfigure}[b]{0.85\textwidth}
		\centering
		\includegraphics[trim = 1cm 2cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
		\caption{First order polynomial regression of fitted parameters as a function of fluid density $\rho_f$}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.85\textwidth}
		\centering
		\includegraphics[trim = 1cm 2cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Trend_Lines_order_2.pdf}
		\caption{Second order polynomial regression of fitted parameters as a function of fluid density $\rho_f$}
	\end{subfigure}
	\caption{Results of parameter fitting, with estimation of the initial state}
\end{figure*}

>>>>

    The parameter estimation problem was solved by fitting the process model to the dataset given in the table \ref{tab: Yield_data}. Each time-series was fitted to the model separately. As a result of fitting, the following parameters were obtained:

    \begin{itemize}
        \item Partition coefficient:\qquad\quad\qquad$k_m$
        \item Internal Diffusion coefficient: \quad$D_i$
        \item Axial Diffusion coefficient: \qquad$D_e^M$
        \item Standard Deviation: \qquad\qquad\quad$\sigma$
    \end{itemize}

    Moreover, the initial state estimation was performed together with parameter estimation. The concentration of solute in the solid phase is assumed to be constant and uniformly distributed. On the other hand, the solute concentration in the fluid phase is assumed not to be uniform and not zero. During the preparation period, when the operating conditions are achieved, the solute diffuses to the fluid phase in contact with the solid particles. Later, the solute in the fluid phase is partially moved (if the pressure increase in the system, the pump cause the movement of the fluid, even if the outlet valve is closed) to the region where there is no solid phase. As a result, the distribution of solutes mass in the fluid phase is assumed to not be uniform, and described by an arbitrary function $H=H(z)$. Some conclusions can be drawn from the analysis of the initial part of each yield curve. It can be noticed that each curve at the beginning has a curvature, which is not linear. In a general sense, it can be said that a quadratic function could approximate the initial part of each extraction curve. A function that, after integration, gives a quadratic-like result is a straight line. Based on that observation, the solute concentration in the fluid phase is assumed to be linearly distributed. The solute concentration is assumed to be zero at the outlet and reach the maximum at the beginning of the fixed bed. The details on the calculation are given in appendix \ref{CH: IC_BC}. The linear distribution can be defined if the total mass of solute $m_{total}$ and partition coefficient $\tau$ are know.

@@

    \begin{itemize}
        \item Total mass of solute: \qquad\qquad\quad$m_{total}$
        \item Partition coefficient: \qquad\qquad\quad$\tau$
    \end{itemize}

	The parameter estimation was run as constrained optimization problem with following constraints:

	\begin{itemize}
		\item $0  \leq k_m   \leq 1$
		\item $0  \leq D_i   \leq +\infty$
		\item $0  \leq D_e^M \leq +\infty$
		\item $76 \leq m_{total} \leq 100$
		\item $0  \leq \tau \leq 1$
		\item $0  \leq \sigma \leq +\infty$
	\end{itemize}

	The results of the parameter estimation can be found in Table \ref{tab: Estimation_results}.

	\begin{table}[H]
		\centering
		\adjustbox{max width=\columnwidth}{%
			\csvautotabular{Figures/Results_estimation/estimation.csv} }
		\caption{Parameter estimation results}
		\label{tab: Estimation_results}
	\end{table}

	The graphical representation of the original

	\begin{figure*}[!h]
		\centering
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[trim = 3cm 11cm 2.5cm 2.1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P200.pdf}
			\caption{Experiment at $40^\circ C$ and $200$ bar}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[trim = 3cm 11cm 2.5cm 2.1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P200.pdf}
			\caption{Experiment at $50^\circ C$ and $200$ bar}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[trim = 3cm 11cm 2.5cm 2.1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P300_org.pdf}
			\caption{Experiment at $40^\circ C$ and $300$ bar}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.8\textwidth}
			\centering
			\includegraphics[trim = 3cm 11cm 2.5cm 2.1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P300_org.pdf}
			\caption{Experiment at $50^\circ C$ and $300$ bar}
		\end{subfigure}
		\caption{Results of parameter fitting, with estimation of the initial state}
	\end{figure*}

	\begin{figure*}[!h]
	\centering
	\begin{subfigure}[b]{0.85\textwidth}
		\centering
		\includegraphics[trim = 1cm 2cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
		\caption{First order polynomial regression of fitted parameters as a function of fluid density $\rho_f$}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.85\textwidth}
		\centering
		\includegraphics[trim = 1cm 2cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Trend_Lines_order_2.pdf}
		\caption{Second order polynomial regression of fitted parameters as a function of fluid density $\rho_f$}
	\end{subfigure}
	\caption{Results of parameter fitting, with estimation of the initial state}
	\end{figure*}
